---
title: "knapsack"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{knapsack}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# Description 

This package is use for three different  methods to use knapsack problem.
In first one we use Bruce force which we do with the help of by making subsets.
second methods is we do with the help of dynamic where we do this with the help of iteration.
Third one is greedy method.



```{r setup}
library(lab6)
```
# Brute Force Knapsack
This function we use to find maximum value with the help of making subsets. function gave us max value and elements as well.
we also use paralization as well in the function which makes the ncores and subsetin we enhance our processing as well.

## Question 1
### *How much time does it take to run brute_force_knapsack for n = 16 objects?*
Brute force computation is slow because loop has go through all the values and will check it if it woks fine or not it will check the possible values to calculate the max value and the time complexity of the algorithm is O(2^n).

This is for non paraliation.

  user       system       elapsed 
  0.846      0.192        1.863 
  
```{r, eval=FALSE}

set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 2000
knapsack_objects <-
data.frame(
w=sample(1:4000, size = n, replace = TRUE),
v=runif(n = n, 0, 10000)
)
system.time(brute_force_knapsack(knapsack_objects[1:16, ], 2000))
```

for parallization
 user                  system                 elapsed 
  0.683                0.139                   1.560 


As we can see paralizzation gives us best one.
```{r, eval=FALSE}

set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 2000
knapsack_objects <-
data.frame(
w=sample(1:4000, size = n, replace = TRUE),
v=runif(n = n, 0, 10000)
)
system.time(brute_force_knapsack(knapsack_objects[1:16, ], 2000), TRUE)
```
# knapsack Dynamic
we use another way to calculate the max value and its index with the help of knapsack dynamic.



## Question 2
### *How much time does it take to run knapsack_dynamic with n = 500 objects?*

This is discret way of solving problem we use a function into function and then used one while loop 
which gives us O(n*W) time complicity.

for specific number we are going to run sys time check

we get   
   user      system          elapsed 
  1.509      0.033            1.586 

```{r, eval=FALSE}

set.seed(42, kind = "Mersenne-Twister", normal.kind = "Inversion")
n <- 2000
knapsack_objects <-
data.frame(
w=sample(1:4000, size = n, replace = TRUE),
v=runif(n = n, 0, 10000)
)
system.time(knapsack_dynamic(knapsack_objects[1:500, ], 2000))
```
